article title

### 2022-08-06 article.tex
Rename bibliography input file
Fix most errors to make article work

% this is the beginning of the preamble section
% must always be first line of a <path.tex> document
\documentclass[10pt, letterpaper, twoside]{article}
\usepackage[utf8]{inputenc}
\usepackage[sfdefault]{noto}
\setlength{\textwidth}{6in}
\setlength{\textheight}{9in}
\setlength{\topmargin}{-1in}
\setlength{\oddsidemargin}{.25in}
\setlength{\evensidemargin}{.25in}

% this package has better control of title, author elements
\usepackage{titling}
\setlength{\droptitle}{-8pt}
\pretitle{\begin{flushleft}\LARGE\bfseries}
\posttitle{\par\end{flushleft}}
\preauthor{\begin{flushleft}\normalsize}
\postauthor{\end{flushleft}}
\predate{\begin{flushleft}\small}
\postdate{\end{flushleft}}
\date{\today}
% edit the following line for the title of the article
\title{article title}
% edit the following line for the author(s) of the article
\author{article author}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}
\raggedbottom
\renewenvironment{abstract}{\par\noindent\textbf{\abstractname}\par}

@@

% very useful for hyperlinks
% useful for Greek letters in text mode
\usepackage[cbgreek]{textgreek}

@@

% useful for the bibliography
\usepackage[style=authoryear]{biblatex}
\addbibresource{pilon_gilles.bib}

% define theorem-like elements
\theoremstyle{myenv}
\theoremstyle{mytheorem}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{axiom}[theorem]{Axiom}
\theoremstyle{mydefinition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{exercise}[theorem]{Exercise}
\newtheorem{question}[theorem]{Question}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{example}[theorem]{Example}
\newtheorem{remark}[theorem]{Remark}
\makeatletter
\@addtoreset{theorem}{section}
\makeatother

@@

\usepackage[unicode]{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=magenta,
    citecolor=green,
    linkcolor=red
}

@@

@@

\newpage
\section{Introduction}\label{sec:introduction}
\renewcommand{\epigraphflush}{flushleft}
\renewcommand{\textflush}{flushleft}
\renewcommand{\sourceflush}{flushleft}
\epigraph{Remember, the objective is to take the right action on the process. No
credit is given for finding the `right numbers.'}{Donald J. Wheeler}

@@

\subsection{Simple table}\label{sec:simple_table}`

@@

\subsection{Multirow table}\label{sec:multirow_table}`
\begin{table}[H]
\footnotesize
\centering
\begin{tabular}{llll}
\toprule
                                           & \textbf{Process requirement}            & \textbf{Sampling}                        & \textbf{Comments} \\
\midrule
\multirow[t]{4}{*}{$C_\text{pk}$}          & - Stable and predictable variation      & - Rational                               & - Possible cost to increasing $C_\text{pk}$ \\
                                           & - Normal distribution                   & - Representative of process              & - Wide confidence interval \\
                                           & - Need at least one specification limit & - Ensure same process conditions         & \\
                                           &                                         & - No identifiable condition changes      & \\
\multirow[t]{4}{*}{$P_\text{pk}$}          & - Stable and predictable variation      & - Random                                 & - Possible cost to increasing ppk \\
                                           & - Normal distribution                   & - Sufficiently large, representative     & - Wide confidence interval \\
                                           & - Need at least one specification limit & - Ensure same process conditions         & - Easiest formulae to explain \\
                                           &                                         & - No identifiable condition changes      & \\
\multirow[t]{4}{*}{$C_\text{pm}$}          & - Stable and predictable variation      & - Same as $C_\text{pk}$ or $P_\text{pk}$ & - $C_\text{pm}$ penalizes for being off-target \\
                                           & - Normal distribution                   &                                          & - Wide confidence interval \\
                                           & - Need at least one specification limit &                                          & - Most difficult formulae to explain \\
                                           & - Need specification target             &                                          & \\
\bottomrule
\end{tabular}
\caption{Comparison of capability indices}
\label{tab:comparison_capability_indices}
\end{table}

@@

\subsection{Inline mathematics}\label{sec:inline_mathematics}`
Examples of inline mathematics $\frac{a}{b}$, followed by text and another inline equation $\lim_{x\to 0}\frac{\sin x}{x}$=1 and more text $\sum_{k=0}^\infty \frac{1}{2^k}=2$ and finally much more text to cover many lines of a paragraph.

@@

@@

\newpage
\listofmylemmas

\newpage
\listofmypropositions

@@

Add files, data, and other supporting information, and where it can be obtained.

>>>>

% this is the beginning of the preamble section
% the next line must always be first line of a <path.tex> document
\documentclass[10pt, letterpaper, twoside]{article}
\usepackage[utf8]{inputenc}
\usepackage[sfdefault]{noto}
\setlength{\textwidth}{6in}
\setlength{\textheight}{9in}
\setlength{\topmargin}{-1in}
\setlength{\oddsidemargin}{.25in}
\setlength{\evensidemargin}{.25in}

% this package has better control of title, author elements
\usepackage{titling}
\setlength{\droptitle}{-8pt}
\pretitle{\begin{flushleft}\LARGE\bfseries}
\posttitle{\par\end{flushleft}}
\preauthor{\begin{flushleft}\normalsize}
\postauthor{\end{flushleft}}
\predate{\begin{flushleft}\small}
\postdate{\end{flushleft}}

% edit the following line to "fix" the data
\date{\today}

% edit the following line for the title of the article
\title{article title}

% edit the following line for the author(s) of the article
\author{article author}

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}
\raggedbottom
\renewenvironment{abstract}{\par\noindent\textbf{\abstractname}\par}

@@

% very useful for hyperlinks
\usepackage[unicode]{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=magenta,
    citecolor=green
}

% required for bibtex URLs
\usepackage{url}

% useful for Greek letters in text mode
\usepackage[cbgreek]{textgreek}

@@

% useful for the bibliography
\usepackage[style=authoryear]{biblatex}
\addbibresource{~/documents/repositories/latex/pilon_gilles_bibliography.bib}

% useful for the glossary
\usepackage[toc, acronym, nopostdot, numberedsection, record=hybrid, shortcuts=ac, abbreviations]{glossaries-extra}
\makeglossaries
\GlsXtrLoadResources[
    src={pilon_gilles_glossary.bib},
    selection={recorded and deps},
    sort=letter-nocase
]

% define theorem-like elements
% \theoremstyle{myenv}
% \theoremstyle{mytheorem}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{axiom}[theorem]{Axiom}
% \theoremstyle{mydefinition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{exercise}[theorem]{Exercise}
\newtheorem{question}[theorem]{Question}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{example}[theorem]{Example}
\newtheorem{remark}[theorem]{Remark}
\makeatletter
\@addtoreset{theorem}{section}
\makeatother

@@

@@

\renewcommand{\epigraphflush}{flushleft}
\renewcommand{\textflush}{flushleft}
\renewcommand{\sourceflush}{flushleft}
\epigraph{A picture is worth a thousand words.}{Anon}

\begin{figure}[H]
\includegraphics[scale=0.25, left]{../fot/matplotlib_anatomy_of_a_figure.png}
\caption{Anatomy of a matplotlib figure}
\end{figure}

@@

\newpage
\section{Introduction}\label{sec:introduction}
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

@@

\subsection{Simple table}\label{sec:simple_table}

@@

\subsection{Multirow table}\label{sec:multirow_table}
\begin{table}[H]
\footnotesize
\centering
\begin{tabular}{llll}
\toprule
                                           & \textbf{Process requirement}            & \textbf{Sampling}                        & \textbf{Comments} \\
\midrule
\multirow[t]{4}{*}{$C_\text{pk}$}          & - Stable and predictable variation      & - Rational                               & - Possible cost to increasing $C_\text{pk}$ \\
                                           & - Normal distribution                   & - Representative of process              & - Wide confidence interval \\
                                           & - Need at least one specification limit & - Ensure same process conditions         & \\
                                           &                                         & - No identifiable condition changes      & \\
\multirow[t]{4}{*}{$P_\text{pk}$}          & - Stable and predictable variation      & - Random                                 & - Possible cost to increasing ppk \\
                                           & - Normal distribution                   & - Sufficiently large, representative     & - Wide confidence interval \\
                                           & - Need at least one specification limit & - Ensure same process conditions         & - Easiest formulae to explain \\
                                           &                                         & - No identifiable condition changes      & \\
\multirow[t]{4}{*}{$C_\text{pm}$}          & - Stable and predictable variation      & - Same as $C_\text{pk}$ or $P_\text{pk}$ & - $C_\text{pm}$ penalizes for being off-target \\
                                           & - Normal distribution                   &                                          & - Wide confidence interval \\
                                           & - Need at least one specification limit &                                          & - Most difficult formulae to explain \\
                                           & - Need specification target             &                                          & \\
\bottomrule
\end{tabular}
\caption{Comparison of capability indices}
\label{tab:comparison_capability_indices}
\end{table}

@@

\subsection{Inline mathematics}\label{sec:inline_mathematics}
Examples of inline mathematics $\frac{a}{b}$, followed by text and another inline equation $\lim_{x\to 0}\frac{\sin x}{x}$=1 and more text $\sum_{k=0}^\infty \frac{1}{2^k}=2$ and finally much more text to cover many lines of a paragraph.

@@

\newpage
\section{Glossary terms}\label{sec:glossary_terms}

Here is a request to fill in \gls{dependent_variable} and \glspl{dependent_variable}.

For dual abbreviations and glossary terms, \gls{anome}.

@@

% \newpage
% \listofmylemmas

% \newpage
% \listofmypropositions

@@

Add files, data, and other supporting information, and where it can be obtained.
all

\newpage
\printunsrtglossary[type={abbreviations}]

\newpage
\printunsrtglossary[style={indexgroup}]
